Topological approach to finding blackholes in directed networks

### 2019-12-06 blackholes/pavt/article.tex
Graphs added
fix
introduction

\section{Blackhole Search in Directed Graph}
applications Anti-Money Laundering \cite{semenov2017survey}

Semenov et al. \cite{semenov2017survey}
in 2017 provided a survey of common approaches to anti - money laundering by graph mining.

The online detection of black holes/volcanos can timely
reflect anomalous events, such as disasters, catastrophic accidents,
and therefore help keep public safety \cite{hong2015detecting}.

@@

>>>>

\section{Blackhole Search in Directed Graph}
The task of pattern mining in directed graphs finds its aplications in different areas. In 2010 Li et al.\cite{li2010mining} state
that governments are interested in detecting cases of financial fraud. They formulate the task for finding cases of illegal collaboration, and introduce dual patterns:
blackhole and volcano. Those appear when a group of traders perform operations only between each other in order to manipulate market.
Continuing study of different financial fraud casese, in 2017 Semenov et al. \cite{semenov2017survey} provided a survey of common approaches to anti - money laundering by graph mining.
There are other applications. For example, the online detection of black holes/volcanos can timely 
reflect anomalous events, such as disasters, catastrophic accidents, and therefore help keep public safety \cite{hong2015detecting}.

@@

\begin{figure}[p]
    \includegraphics[width=\linewidth]{rmat.png}
    \caption{RMAT}
    \label{fig:rmat}
\end{figure}
\begin{figure}[p]
    \includegraphics[width=\linewidth]{ssca2.png}
    \caption{SSCA2}
    \label{fig:ssca2}
\end{figure}
\begin{figure}[p]
    \includegraphics[width=\linewidth]{ur.png}
    \caption{UR}
    \label{fig:ur}
\end{figure}
